Supplementary materials

### 2018-02-27 publication/manuscript.Rmd
Compare models global vs community

Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(tab:table-species-gain-global)). 
When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(tab:table-species-gain-site); Figure \@ref(fig:fig-conspecific-per-site) and \@ref(fig:fig-conspecific-per-plant)). 
Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)).

>>>>

Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(tab:table-species-gain-global)). 
When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(tab:table-species-gain-site); Figure \@ref(fig:fig-conspecific-per-site) and \@ref(fig:fig-conspecific-per-plant)). 
Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)). 
When comparing the performance of the models constructed at the community or study-wide level we found that the gain in conspecific pollen was better predicted by the community level models, while the gain in heterospecific pollen was better predicted by the study-wide models (Table \@ref(S-tab:table-global-vs-community-models).

### 2018-02-27 publication/supp_info.Rmd
Compare models global vs community

cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)

>>>>

cowplot::plot_grid(p2, p1, rel_widths = c(0.42, 0.58), labels = LETTERS[1:2], label_size = 8)
```{r table-global-vs-community-models, results = 'asis'}
loadd(wilcox_glo_com)

wilcox_glo_com %>%
  filter(quality %in% c("rmse", "sigma"), 
         var_trans == "log") %>%
  select(quality, pollen_category, min_scale, estimate, p.value) %>%
  rename(`model metric` = quality,
         `pollen type` = pollen_category, 
         `best model set` = min_scale,
         `shift estimate` = estimate, 
         `p value` = p.value) %>%
  xtable(digits = -1, caption = "Results of two sample paired Wilcoxon signed rank test comparing the root mean square error and the residual standard deviation of the model sets constructed using predictors computed at the community or study level.", 
         label = "tab:table-global-vs-community-models")
```
